---
params:
  output_dir: "/nfs/data/Applications/Ambulatory/"
output:
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
    fig_width: 7
    fig_height: 6
resource_files:
- hh_crosswalk.csv
- Rad_Onc_Data.csv
- Radiology_Data.csv
- Radiology_Site_Mapping.csv
- Epic Department Mapping Correction.csv
- hh_crosswalk.csv
- Radiology_Data.csv
- Rad_Onc_Data.csv
- Radiology_Site_Mapping.csv
- Epic Department Mapping Correction.csv
- open_encounters_exclusion.xlsx
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: auto;
  margin-right: auto;
}
</style>
<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>
<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>
<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
</style>
```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
suppressMessages({
  memory.limit(size = 100000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```


```{r Connect to Data Source, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)

access_raw_tbl <- tbl(conn1, "MV_DM_PATIENT_ACCESS")
                      
```


```{r Global Functions, echo = FALSE, warning = FALSE, message = FALSE}

'%!in%' <- function(x,y)!('%in%'(x,y))

```


```{r Global Variables, echo = FALSE, warning = FALSE, message = FALSE}

report_run_date <- Sys.Date()

todays_year <- year(Sys.Date())
prior_year <- year(Sys.Date())-1

date_start <- as.Date(paste0(year(Sys.Date())-1,"-01-01"))
date_end <- as.Date(paste0(year(Sys.Date()),"-12-31"))

date_start_formatted <- paste0(format(as.Date(date_start), "%Y-%m-%d"), " 00:00:00")
date_end_formatted <- paste0(format(as.Date(date_start), "%Y-%m-%d"), " 00:00:00")

monthOptions <- c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")

# Missing Charges Date Cutoff ------------------
business_days <- seq(date_start, date_end, by="days")[!is.weekend(seq(date_start, date_end, by="days"))]
missing_chg_cutOff <- business_days[length(business_days)-3] # Should this be 2 or 3?

```


```{r Import HH Data, echo = FALSE, warning = FALSE, message = FALSE}
# Run Locally -----------------------------
# con_hh <- odbcConnect("handhygiene") # Connect to Server
# hh_data_comp_raw <- sqlQuery(con_hh, "SELECT * FROM qidm_dev.dbo.amb_hand_hygiene_comp") # Master Referrals Data
# hh_data_comp_raw_pt_entry <- sqlQuery(con_hh, "SELECT * FROM qidm_dev.dbo.PT_AMB_HAND_HYGIENE_COMP") # Master Referrals Data


# Run on Server ---------------------------
con_hh <- dbConnect(odbc(),
                    Driver = "SQLServer",
                    Server = "10.2.42.69",
                    UID = "kweons01",
                    PWD = "Pasword01#PasPasword01#Pas",
                    Port = 1433)
hh_data_comp_raw <- dbGetQuery(con_hh, "SELECT * FROM qidm_dev.dbo.amb_hand_hygiene_comp")
hh_data_comp_raw <- as.data.frame(hh_data_comp_raw)

hh_data_comp_raw_pt_entry <- dbGetQuery(con_hh, "SELECT * FROM qidm_dev.dbo.PT_AMB_HAND_HYGIENE_COMP")
hh_data_comp_raw_pt_entry <- as.data.frame(hh_data_comp_raw_pt_entry)


# Import HH Data Mapping ------------------
hh_crosswalk <- as.data.frame(read_csv("/nfs/data/Applications/Ambulatory/hh_crosswalk.csv"))
# hh_crosswalk <- as.data.frame(read_csv(file.choose()))
 
```


```{r Radiology and Rad Onc Data, echo = FALSE, warning = FALSE, message = FALSE}

# Import Radiology and Rad Onc Data -------------------
rad_onc_data_raw <- as.data.frame(read.csv("/nfs/data/Applications/Ambulatory/Rad_Onc_Data.csv"))
radiology_data_raw <- as.data.frame(read.csv("/nfs/data/Applications/Ambulatory/Radiology_Data.csv"))
radiology_ref <- as.data.frame(read.csv("/nfs/data/Applications/Ambulatory/Radiology_Site_Mapping.csv"))


## Import Locally -------------------------------------
# rad_onc_data_raw <- as.data.frame(read.csv("Rad_Onc_Data.csv"))
# radiology_data_raw <- as.data.frame(read.csv("Radiology_Data.csv"))
# radiology_ref <- as.data.frame(read.csv("Radiology_Site_Mapping.csv"))


# Process Radiology + Rad Onc Data --------------------
## Rad Onc Data 
rad_onc_data_raw <- rad_onc_data_raw %>%
  mutate_at(c('MSBI', 'MSH.MSDFP', 'MSUS', 'MSW'), as.numeric) %>%
  mutate(Campus.Specialty = "Radiation Oncology",
         Department = "Radiation Oncology",
         Appt.Year = format(as.Date(as.yearmon(Month, "%b-%y"), format = "%b %y"),"%Y"),
         Appt.MonNum = as.numeric(format(as.Date(as.yearmon(Month, "%b-%y"), format = "%b %y"),"%m")),
         Appt.Month = format(as.Date(as.yearmon(Month, "%b-%y"), format = "%b %y"),"%b"),
         Visit.Method = "IN PERSON") %>%
  dplyr::select(-Month) %>%
  pivot_longer(MSBI:MSW,
               names_to = "Campus",
               values_to = "monthly_vol") %>%
  mutate(Campus = ifelse(Campus == "MSH.MSDFP","MSH-MSDFP",Campus))


# Process Radiology Data
radiology_data_raw[,2:length(radiology_data_raw)] <-lapply(radiology_data_raw[,2:length(radiology_data_raw)],as.numeric)
radiology_data_raw <- radiology_data_raw %>%
  pivot_longer(BC:UC,
               names_to = "Campus",
               values_to = "monthly_vol")

radiology_data_raw$Campus <- radiology_ref$Campus[match(radiology_data_raw$Campus, radiology_ref$ID)]

radiology_data_raw <- radiology_data_raw %>%
  group_by(Month, Campus) %>%
  summarise(monthly_vol = sum(monthly_vol)) %>%
  mutate(Campus.Specialty = "Radiology",
         Department = "Radiology",
         Appt.Year = format(as.Date(as.yearmon(Month, "%b-%y"), format = "%b %y"),"%Y"),
         Appt.MonNum = as.numeric(format(as.Date(as.yearmon(Month, "%b-%y"), format = "%b %y"),"%m")),
         Appt.Month = format(as.Date(as.yearmon(Month, "%b-%y"), format = "%b %y"),"%b"),
         Visit.Method = "IN PERSON") %>%
  dplyr::select(-Month) %>%
  arrange(Appt.Year, Appt.MonNum)


# Merge Rad Onc and Radiology Data 
rad_radOnc_data <- bind_rows(rad_onc_data_raw, radiology_data_raw)

rad_radOnc_data <- rad_radOnc_data %>%
  mutate(Campus = toupper(Campus)) %>%
  filter(Appt.Year %in% c(prior_year, todays_year)) %>%
  group_by(Campus, Appt.Year, Appt.Month) %>%
  summarise(total = sum(monthly_vol))


# Filter out Sites --------------------------
rad_radOnc_data <- rad_radOnc_data %>%
  filter(!Campus %in% c("MSB", "MS NOW", "MSHP", "OTHER")) 

rad_onc_date <- paste0(rad_onc_data_raw[nrow(rad_onc_data_raw),"Appt.Month"],", ", rad_onc_data_raw[nrow(rad_onc_data_raw),"Appt.Year"])
radiology_date <- paste0(radiology_data_raw[nrow(radiology_data_raw),"Appt.Month"],", ", radiology_data_raw[nrow(radiology_data_raw),"Appt.Year"])

```


```{r Hand Hygiene Data Processing, echo = FALSE, warning = FALSE, message = FALSE}

# Processs RedCap Data --------------------------
## Format Column Names --------------------
colnames(hh_data_comp_raw) <- tolower(colnames(hh_data_comp_raw))


# Manuallyt Map Site Information ---------
## Map MSD units
hh_data_comp_raw$site<- ifelse(hh_data_comp_raw$site == "MSD",
                                hh_crosswalk$unit[match(trim(hh_data_comp_raw$msd_unit), trim(hh_crosswalk$Location))], hh_data_comp_raw$site)
## Map msh_unit
hh_data_comp_raw$site<- ifelse(hh_data_comp_raw$site == "MSH",
                                hh_crosswalk$unit[match(trim(hh_data_comp_raw$msh_unit), trim(hh_crosswalk$Location))], hh_data_comp_raw$site)

hh_data_comp <- hh_data_comp_raw %>%
  dplyr::select(-language) %>%
  pivot_longer(
    c("msb_unit","msh_unit","msd_unit","nyee_unit","msq_unit","msm_unit","msw_unit","net_unit"),
    names_to = "unit_site",
    values_to = "unit"
  ) %>%
  filter(date != "NULL") %>%
  mutate_if(is.numeric, as.character) %>%
  filter(!is.na(site))


# Process Patient Entry Data --------------------
colnames(hh_data_comp_raw_pt_entry) <- tolower(colnames(hh_data_comp_raw_pt_entry))
hh_data_comp_pt_entry <- hh_data_comp_raw_pt_entry %>%
  rename(date = data_date) %>%
  mutate(site = ifelse(site == "MSH", "MSDFP", site)) %>%
  mutate_if(is.numeric, as.character) 

hh_data_comp_pt_entry$date <- as.character(hh_data_comp_pt_entry$date)
hh_data_comp <- bind_rows(hh_data_comp, hh_data_comp_pt_entry)



# Merge RedCap and Patient Entry Data -----------
hh_data_merged <- hh_data_comp %>%
  filter(!site %in% c("MS NOW", "MSHP", "NYEE", "MSQ","OTHER","MSB")) %>%
  filter(!is.na(site)) %>%
  dplyr::select(site, unit, date, worker___1, worker___2, worker___3, provider_hands_bef, provider_hands_aft, nurse_hands_bef, nurse_hands_aft, mt_hands_bef, mt_hands_aft) %>%
  mutate(across(4:12, as.numeric)) %>%
  mutate_if(is.numeric, ~ifelse(is.na(.),0,.)) %>%
  mutate_if(is.numeric, ~ifelse(.==2,0,.)) %>%
  group_by(site, unit, date) %>%
  summarise(worker___1 = sum(worker___1),
            worker___2 = sum(worker___2),
            worker___3 = sum(worker___3),
            provider_hands_bef = sum(provider_hands_bef),
            provider_hands_aft = sum(provider_hands_aft),
            nurse_hands_bef = sum(nurse_hands_bef),
            nurse_hands_aft = sum(nurse_hands_aft),
            mt_hands_bef = sum(mt_hands_bef),
            mt_hands_aft = sum(mt_hands_aft)) %>%
  mutate(date = as.Date(date, "%Y-%m-%d"),
         Appt.Year = as.numeric(format(as.Date(date, "%Y-%m-%d"),"%Y")),
         Appt.WeekNum = lubridate::epiweek(as.Date(date, "%Y-%m-%d"))) %>%
  filter(Appt.Year >= as.numeric(prior_year))

hh_data_merged_role <- hh_data_comp %>%
  dplyr::select(site, unit, date, provider_hands_bef, provider_hands_aft, nurse_hands_bef, nurse_hands_aft, mt_hands_bef, mt_hands_aft) %>%
  pivot_longer(provider_hands_bef: mt_hands_aft,
               names_to = "role",
               values_to = "compliance") %>%
  mutate(date = as.Date(date, "%Y-%m-%d"),
         Appt.Year = as.numeric(format(as.Date(date, "%Y-%m-%d"),"%Y")),
         Appt.WeekNum = lubridate::epiweek(as.Date(date, "%m/%d/%Y")),
         compliance = ifelse(compliance == 2,0,compliance)) %>%
  filter(compliance != "") %>%
  filter(compliance != 2) %>%
  filter(Appt.Year >= as.numeric(prior_year)) %>%
  group_by(site, unit, date, Appt.Year, Appt.WeekNum, role, compliance) %>%
  summarise(total_obs = n())%>%
  mutate(compliance = ifelse(compliance == 0, "No", "Yes"),
         total_obs = as.numeric(total_obs)) %>%
  pivot_wider(
    names_from = compliance,
    values_from = total_obs,
    values_fill=list(total_obs=0)) %>%
  ungroup() %>%
  mutate(total_obs = `Yes`+`No`)
  

# Manually Format NET to NETWORK ------------------------
hh_data_merged <- hh_data_merged %>%
  mutate(site = ifelse(site == "NET","NETWORK",site)) %>%
  arrange(date) %>%
  filter(unit != "NULL")
hh_data_merged_role <- hh_data_merged_role %>%
  mutate(site = ifelse(site == "NET","NETWORK",site)) %>%
  arrange(date) %>%
  filter(unit != "NULL")
hh_data_merged <- hh_data_merged %>%
  mutate(site = ifelse(unit == "UCC", "MSUS",site))

```


```{r Scheduling Data Processing, echo = FALSE, warning = FALSE, message = FALSE}

scheduling_data <- access_raw_tbl %>%
  filter(!is.na(SITE)) %>%
  mutate(Campus = case_when(SITE == "MSDD" ~ "MSDMG",
                            TRUE ~ SITE),
         Campus = case_when(DEPARTMENT_NAME %in% c("1176 5TH DUBIN MED ONC", "1176 5TH DUBIN SURG ONC") ~ "DUBIN",
                            DEPARTMENT_NAME %in% c("1468 MADISON CANCER", "1470 MADISON CANCER CENTER", "10 E 102ND ST INFUSION WHITE BAG", "THERAPEUTIC INF") ~ "RTC",
                            TRUE ~ Campus)) %>%
  filter(!Campus %in% c("MSB", "MS NOW", "MSHP", "OTHER", "DUBIN", "RTC")) %>%
  mutate(Appt.DateYear = TO_DATE(CONTACT_DATE),
         Appt.Year = year(CONTACT_DATE),
         Appt.MonNum = month(CONTACT_DATE)) %>%
  mutate(Visit.Method  = ifelse(VISIT_METHOD == "IN PERSON", "IN PERSON", "TELEHEALTH"),
         New.PT3 = ifelse(is.na(LOS_NAME), NA, ifelse(LOC_NAME %like% "INITIAL|NEW", "New", "Established")),
         enc.status = ifelse(ENC_CLOSED_CHARGE_STATUS %in% c("OPEN", "CLOSED BUT COSIGN NEEDED"), 'OPEN', 'CLOSED')) %>%
  mutate(open.days = ifelse(enc.status == "OPEN", 
                            TO_DATE(lubridate::today()) - TO_DATE(CONTACT_DATE),
                            TO_DATE(Y_ENC_CLOSE_TIME) - TO_DATE(CONTACT_DATE))) %>%
  mutate(Provider = trim(REGEXP_REPLACE(PROV_NAME_WID, "\\[.*?\\]", "" ))) 
  
```


# System Huddle Ambulatory Report
*Report run date: `r report_run_date`*<br/>
*Rad Onc and Radiology data included only in monthly volumes.*<br/>
*Data excludes eIDX, MD Office data.*<br/>
*Data excludes RTC and Dubin data.*<br/>
________________________________________________________________________________________________________________________________________________
<br/>

## Metrics Overview
### 1.Open Encounters Trending
```{r Open Encounters Metric Trending by Site 3, fig.width=12, fig.height = 5, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}

# EPIC Open Encounters Exclusion Criteria ---------------------------------
missing_exc_dept <- read_excel("/nfs/data/Applications/Ambulatory/open_encounters_exclusion_dept.xlsx")
missing_exc_resource <- read_excel("/nfs/data/Applications/Ambulatory/open_encounters_exclusion_res.xlsx")
missing_exc_visitType <- read_excel("/nfs/data/Applications/Ambulatory/open_encounters_exclusion_visit.xlsx")

# missing_exc_dept <- read_excel("open_encounters_exclusion_dept.xlsx")
# missing_exc_resource <- read_excel("open_encounters_exclusion_res.xlsx")
# missing_exc_visitType <- read_excel("open_encounters_exclusion_visit.xlsx")

exc_depts <- unique(missing_exc_dept$DEPARTMENT)
exc_providers <- unique(missing_exc_resource$PROVIDER)


missing_chg_cutOff <- paste0(format(as.Date(missing_chg_cutOff), "%Y-%m-%d"), " 00:00:00")


missing_chg_data <- scheduling_data %>%
  filter(Appt.Year >= prior_year) %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  filter(VISIT_PROV_STAFF_RESOURCE_C == 1) %>%
  filter(TO_DATE(missing_chg_cutOff,"YYYY-MM-DD HH24:MI:SS") >= APPT_DTTM) %>%
  mutate(clo.5days = ifelse(open.days <= 5, 'YES', 'NO')) %>%
  group_by(Campus, DEPARTMENT_NAME, Provider, PRC_NAME, Appt.Year, Appt.MonNum, enc.status, clo.5days) %>%
  summarise(total = n()) %>%
  collect()
  
missing_chg_data <- missing_chg_data %>% 
  filter(DEPARTMENT_NAME %!in% exc_depts) %>%
  filter(Provider %!in% exc_providers) %>%
  filter(!str_detect(PRC_NAME, "ECHO|SOCIAL|NURSE|NUTRITION|LAB|TREATMENT")) %>%
  mutate(Appt.Month = format(as.Date(paste0(Appt.MonNum, "-01-", Appt.Year), "%m-%d-%Y"), "%b")) %>%
  mutate(Appt.Year = as.character(Appt.Year)) %>%
  mutate(Appt.MonthYear = paste0(Appt.Month,"-",Appt.Year))

missing_chg_data_trend_5days <- missing_chg_data %>%
  group_by(Campus, Appt.Year, Appt.MonNum, Appt.MonthYear, enc.status, clo.5days) %>%
  summarise(total = n()) %>%
  collect() %>%
  group_by(Campus, Appt.Year, Appt.MonthYear) %>%
  mutate(total.enc = sum(total)) %>%
  pivot_wider(names_from = clo.5days,
              values_from = total,
              values_fill = 0) %>%
  mutate(clo.5days.perc = round((YES/(total.enc))*100,0)) %>%
  filter(enc.status == "CLOSED")


missing_chg_data_trend_downtown_5days <- missing_chg_data %>%
  filter(Campus %in% c("MSUS","MSDMG","MSBI")) %>%
  mutate(Campus = "MS Downtown") %>%
  group_by(Campus, Appt.MonthYear, enc.status, clo.5days) %>%
  summarise(total = n()) %>%
  group_by(Campus, Appt.MonthYear) %>%
  mutate(total.enc = sum(total)) %>%
  collect() %>%
  pivot_wider(names_from = clo.5days,
              values_from = total,
              values_fill = 0) %>%
  mutate(clo.5days.perc = round((YES/(total.enc))*100,0)) %>%
  filter(enc.status == "CLOSED")


# missing_chg_data_trend_5days <- as.data.frame(readRDS("/nfs/data/Applications/Ambulatory/Data_Updated/missing_chg_data_trend_5days.rds"))
# missing_chg_data_trend_downtown_5days <- as.data.frame(readRDS("/nfs/data/Applications/Ambulatory/Data_Updated/missing_chg_data_trend_downtown_5days.rds"))

```


```{r Open Encounters (5 Days) Metric Trending by Site Output, fig.width=12, fig.height = 5, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}
# Total Encounters and % Closed within 7 Days by Site
map(unique(missing_chg_data_trend_5days$Campus), function(x){
highchart() %>%
  hc_yAxis_multiples(
    list(title = list(text = "Total Encounters"), lineWidth = 3),
    list(title = list(text = "% of Encounters"), showLastLabel = FALSE, opposite = TRUE)
  ) %>%
  hc_xAxis(title = list(text = ""),
           categories = (missing_chg_data_trend_5days %>% filter(Campus == x))$Appt.MonthYear,
           type = "datetime",
           labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name = "Total Encounters",
                data = (missing_chg_data_trend_5days %>% filter(Campus == x))$total.enc,
                type = 'column',
                color='#212070',
                dataLabels = list(enabled = TRUE, format='{point.y}')) %>%
  hc_add_series(name = "% Encounters Closed <=5 Days",
                data = (missing_chg_data_trend_5days %>% filter(Campus == x))$clo.5days.perc,
                type = "line", yAxis = 1,
                color='#d80b8c',
                lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE, format='{point.y}%')) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = paste0(x, " - % Encounters Closed <=5 Days"), align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  hc_subtitle(text = paste0("Excludes Radiology and Rad Onc visits <br>",
                            "Includes Epic provider visits only <br>",
                            "Based on visits from ",date_start," to ",missing_chg_cutOff),
              align = "left", style = list(fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")
}) %>%
  hw_grid(ncol = 2, rowheight = 400) %>% htmltools::browsable()

# rm(missing_chg_data_trend_5days)
# invisible(gc())

```
--------------------------------------------------------------------------------
```{r Open Encounters (5 Days) Metric Trending Summarized, fig.width=12, fig.height = 5, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}

# Based on Metric % Encounteres Closed <=7 days
map(unique(missing_chg_data_trend_downtown_5days$Campus), function(x){
highchart() %>%
  hc_yAxis_multiples(
    list(title = list(text = "Total Encounters"), lineWidth = 3),
    list(title = list(text = "% of Encounters"), showLastLabel = FALSE, opposite = TRUE)
  ) %>%
  hc_xAxis(title = list(text = ""),
           categories = missing_chg_data_trend_downtown_5days$Appt.MonthYear,
           type = "datetime",
           labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name = "Total Encounters",
                data = (missing_chg_data_trend_downtown_5days %>% filter(Campus == x))$total.enc,
                type = 'column',
                color='#212070',
                dataLabels = list(enabled = TRUE, format='{point.y}')) %>%
  hc_add_series(name = "% Encounters Closed <=5 Days",
                data = (missing_chg_data_trend_downtown_5days %>% filter(Campus == x))$clo.5days.perc,
                type = "line", yAxis = 1,
                color='#d80b8c',
                lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE, format='{point.y}%')) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = paste0(x, " - % Encounters Closed <=5 Days"), align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  hc_subtitle(text = paste0("Includes MSUS, MSDMG, and MSBI <br>",
                            "Includes Epic provider visits only <br>",
                            "Excludes Radiology and Rad Onc visits <br>", "Based on visits from ",date_start," to ",missing_chg_cutOff),
              align = "left", style = list(fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")
}) %>%
  hw_grid(ncol = 2, rowheight = 450) %>% htmltools::browsable()


rm(missing_chg_data_trend_downtown_5days)
invisible(gc())
```


### 2. Visit Volume Variance Trending
```{r Volume Variance to 2019 Metric Trending by Site, echo = FALSE, warning = FALSE, message = FALSE}

# Format Data --------------------------
vol_trending <- scheduling_data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  filter(TO_DATE(date_start_formatted, "YYYY-MM-DD HH24:MI:SS") <= APPT_DTTM) %>%
  # filter(TO_DATE(date_end_formatted, "YYYY-MM-DD HH24:MI:SS") <= APPT_DTTM) %>%
  group_by(Campus, Appt.Year, Appt.MonNum) %>%
  summarise(total = n()) %>%
  collect() %>%
  mutate(Appt.Month = format(as.Date(paste0(Appt.MonNum, "-01-", Appt.Year), "%m-%d-%Y"), "%b")) %>%
  mutate(Appt.Year = as.character(Appt.Year))


# Merge with radiology and rad onc monthly volume
vol_trending <- bind_rows(vol_trending, rad_radOnc_data)
vol_trending <- vol_trending %>%
  group_by(Campus, Appt.Year, Appt.Month) %>%
  summarise(total = sum(total)) %>%
  pivot_wider(names_from = Appt.Year,
              values_from = total) %>%
  # mutate(target_5_perc = round(`2022`*1.05)) %>%
  arrange(factor(Appt.Month, levels = monthOptions)) %>%
  arrange(Campus) %>%
  mutate(perc_change = round(((`2024` - `2023`)/`2023`)*100, 0))


# Output Graphs ------------------------
map(unique(vol_trending$Campus), function(x){
highchart() %>%
  hc_yAxis_multiples(
    list(title = list(text = "Total Visits"), lineWidth = 3, min = 0),
    list(title = list(text = "% Change from Prior Year"), min = -50,max=200,
           labels = list(format = '{value}%'),
           showLastLabel = FALSE, opposite = TRUE)
  ) %>%
  hc_xAxis(title = list(text = ""),
           categories = (vol_trending %>% filter(Campus == x))$Appt.Month,
           type = "datetime",
           labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name   = "2023 Total Visits",
                data   = (vol_trending %>% filter(Campus == x))$`2023`,
                # type = 'column',
                # color = '#a5a7a5'
                marker = list(enabled= TRUE),
                color='#a5a7a5',
                lineWidth=3,
                lineColor='#a5a7a5'
                ) %>%
  hc_add_series(name = "2024 Total Visits",
                data   = (vol_trending %>% filter(Campus == x))$`2024`,
                marker = list(enabled= TRUE),
                color='#212070',
                lineWidth=3,
                lineColor='#212070'
                ) %>%
  hc_add_series(name = "% Change from Prior Year",
                data = (vol_trending %>% filter(Campus == x))$perc_change,
                type = "column", yAxis = 1,
                                zones = list(list(value = 0,
                                  color = 'red')),
                color='#00b800',
                # lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE, format='{point.y}%')) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
    hc_title(text = paste0(x, " - Visit Volume Variance"), align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
    hc_subtitle(text = paste0("Includes Radiology and Rad Onc visits up to ",radiology_date,"<br> Based on visits from ",date_start," to ",date_end),
              align = "left", style = list(fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
    hc_tooltip(shared = TRUE, borderColor = "black")
  }) %>%
  hw_grid(ncol = 2, rowheight = 400) %>% htmltools::browsable()

```

--------------------------------------------------------------------------------

```{r Volume Variance to 2019 Metric Trending Summarized, echo = FALSE, warning = FALSE, message = FALSE}

# Format Data --------------------------
vol_trending_downtown <- scheduling_data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  filter(TO_DATE(date_start_formatted, "YYYY-MM-DD HH24:MI:SS") <= APPT_DTTM) %>%
  # filter(TO_DATE(date_end_formatted, "YYYY-MM-DD HH24:MI:SS") <= APPT_DTTM) %>%
  group_by(Campus, Appt.Year, Appt.MonNum) %>%
  summarise(total = n()) %>%
  collect() %>%
  mutate(Appt.Month = format(as.Date(paste0(Appt.MonNum, "-01-", Appt.Year), "%m-%d-%Y"), "%b")) %>%
  mutate(Appt.Year = as.character(Appt.Year))


# Merge with radiology and rad onc monthly volume
vol_trending_downtown <- bind_rows(vol_trending_downtown, rad_radOnc_data)
vol_trending_downtown <- vol_trending_downtown %>%
  filter(Campus %in% c("MSUS","MSDMG","MSBI")) %>%
  mutate(Campus = "MS Downtown") %>%
  group_by(Campus, Appt.Year, Appt.Month) %>%
  summarise(total = sum(total)) %>%
  pivot_wider(names_from = Appt.Year,
              values_from = total) %>%
  # mutate(target_5_perc = round(`2022`*1.05)) %>%
  arrange(factor(Appt.Month, levels = monthOptions)) %>%
  arrange(Campus) %>%
  mutate(perc_change = round(((`2024` - `2023`)/`2023`)*100, 0))


# Output Graphs ------------------------
map(unique(vol_trending_downtown$Campus), function(x){
highchart() %>%
  hc_yAxis_multiples(
    list(title = list(text = "Total Visits"), lineWidth = 3, min = 0),
    list(title = list(text = "% Change from Prior Year"), min = -50,max=200,
           labels = list(format = '{value}%'),
           showLastLabel = FALSE, opposite = TRUE)
  ) %>%
  hc_xAxis(title = list(text = ""),
           categories = (vol_trending_downtown %>% filter(Campus == x))$Appt.Month,
           type = "datetime",
           labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name   = "2022 Total Visits",
                data   = (vol_trending_downtown %>% filter(Campus == x))$`2022`,
                # type = 'column',
                # color = '#a5a7a5'
                marker = list(enabled= TRUE),
                color='#a5a7a5',
                lineWidth=3,
                lineColor='#a5a7a5'
                ) %>%
  hc_add_series(name = "2023 Total Visits",
                data   = (vol_trending_downtown %>% filter(Campus == x))$`2023`,
                marker = list(enabled= TRUE),
                color='#212070',
                lineWidth=3,
                lineColor='#212070'
                ) %>%
  hc_add_series(name = "% Change from Prior Year",
                data = (vol_trending_downtown %>% filter(Campus == x))$perc_change,
                type = "column", yAxis = 1,
                                zones = list(list(value = 0,
                                  color = 'red')),
                color='#00b800',
                # lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE, format='{point.y}%')) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
    hc_title(text = paste0(x, " - Visit Volume Variance"), align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
    hc_subtitle(text = paste0("Includes MSUS, MSDMG, and MSBI <br>","Includes Radiology and Rad Onc visits up to ",radiology_date,
                              "<br> Based on visits from ",date_start," to ",date_end),
              align = "left", style = list(fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
    hc_tooltip(shared = TRUE, borderColor = "black")
  }) %>%
  hw_grid(ncol = 2, rowheight = 450) %>% htmltools::browsable()


rm(vol_trending)
rm(vol_trending_downtown)
invisible(gc())
```


### 3. New Patient Ratio Trending
```{r New Patient Volume Trending by Site, echo = FALSE, warning = FALSE, message = FALSE}

# Format Data ------------------------------
new_vol <- scheduling_data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  filter(TO_DATE(date_start_formatted, "YYYY-MM-DD HH24:MI:SS") <= APPT_DTTM) %>%
  group_by(Campus, Appt.Year, Appt.MonNum, LOS_NAME) %>%
  summarise(total = n()) %>%
  collect() %>%
  mutate(New.PT3 = ifelse(str_detect(LOS_NAME, "NEW|INITIAL"), "New", "Established"))


new_vol_trending <- new_vol %>%
  group_by(Campus, Appt.Year, Appt.MonNum, New.PT3) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = New.PT3,
              values_from = total,
              values_fill = 0) %>%
  mutate(total_vol = `New` + `Established`,
         new_perc = round((New/(total_vol))*100,0)) %>%
  mutate(Appt.Month = format(as.Date(paste0(Appt.MonNum, "-01-", Appt.Year), "%m-%d-%Y"), "%b")) %>%
  mutate(Appt.Year = as.character(Appt.Year)) %>%
  mutate(Appt.MonthYear = paste0(Appt.Month,"-",Appt.Year))

# new_vol_trending <- as.data.frame(readRDS("/nfs/data/Applications/Ambulatory/Data_Updated/new_vol_trending.rds"))

  
# Output Graphs -----------------------------
map(unique(new_vol_trending$Campus), function(x){
highchart() %>%
  hc_yAxis_multiples(
    list(title = list(text = "Total Visits"), lineWidth = 3),
    list(title = list(text = "% of New Visits"), labels = list(format = '{value}%'),
         showLastLabel = FALSE, opposite = TRUE)
  ) %>%
  hc_xAxis(title = list(text = ""),
           # categories = (new_vol_trending %>% filter(Campus == x))$Appt.MonthYear,
           categories = new_vol_trending$Appt.MonthYear,
           type = "datetime",
           labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name = "Total Visits",
                data = (new_vol_trending %>% filter(Campus == x))$total_vol,
                type = 'column',
                color='#212070',
                dataLabels = list(enabled = TRUE, format='{point.y}')) %>%
  hc_add_series(name = "% New Visits",
                data = (new_vol_trending %>% filter(Campus == x))$new_perc,
                type = "line", yAxis = 1,
                color='#d80b8c',
                lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE, format='{point.y}%')) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = paste0(x, " - % New Visits"), align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  hc_subtitle(text = paste0("Excludes Radiology and Rad Onc visits <br>", "Based on visits from 2023-01-01"," to ",date_end),
              align = "left", style = list(fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")
}) %>%
  hw_grid(ncol = 2, rowheight = 400) %>% htmltools::browsable()
```

--------------------------------------------------------------------------------
```{r New Patient Volume Trending Summarized, echo = FALSE, warning = FALSE, message = FALSE}

# Format Data ------------------------------
new_vol_trending_downtown <- new_vol %>%
  filter(Campus %in% c("MSUS","MSDMG","MSBI")) %>%
  mutate(Campus = "MS Downtown") %>%
  group_by(Campus, Appt.Year, Appt.MonNum, New.PT3) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = New.PT3,
              values_from = total,
              values_fill = 0) %>%
  mutate(total_vol = `New` + `Established`,
         new_perc = round((New/(total_vol))*100,0)) %>%
  mutate(Appt.Month = format(as.Date(paste0(Appt.MonNum, "-01-", Appt.Year), "%m-%d-%Y"), "%b")) %>%
  mutate(Appt.Year = as.character(Appt.Year)) %>%
  mutate(Appt.MonthYear = paste0(Appt.Month,"-",Appt.Year))

# new_vol_trending_downtown <- as.data.frame(readRDS("/nfs/data/Applications/Ambulatory/Data_Updated/new_vol_trending_downtown.rds"))


# Output Graphs ------------------------------
map(unique(new_vol_trending_downtown$Campus), function(x){
highchart() %>%
  hc_yAxis_multiples(
    list(title = list(text = "Total Visits"), lineWidth = 3),
    list(title = list(text = "% of New Visits"), labels = list(format = '{value}%'),
         showLastLabel = FALSE, opposite = TRUE)
  ) %>%
  hc_xAxis(title = list(text = ""),
           # categories = (new_vol_trending_downtown %>% filter(Campus == x))$Appt.MonthYear,
           categories = new_vol_trending_downtown$Appt.MonthYear,
           type = "datetime",
           labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name = "Total Visits",
                data = (new_vol_trending_downtown %>% filter(Campus == x))$total_vol,
                type = 'column',
                color='#212070',
                dataLabels = list(enabled = TRUE, format='{point.y}')) %>%
  hc_add_series(name = "% New Visits",
                data = (new_vol_trending_downtown %>% filter(Campus == x))$new_perc,
                type = "line", yAxis = 1,
                color='#d80b8c',
                lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE, format='{point.y}%')) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = paste0(x, " - % New Visits"), align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  hc_subtitle(text = paste0("Excludes Radiology and Rad Onc visits <br>", "Based on visits from 2023-01-01"," to ",date_end),
              align = "left", style = list(fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")
}) %>%
  hw_grid(ncol = 2, rowheight = 450) %>% htmltools::browsable()

invisible(gc())
```

### 5. Hand Hygiene Trending
```{r Hand Hygiene Metric Trending by Site, fig.width=12, fig.height = 5, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}

hh_site <- hh_data_merged %>%
  mutate(Month = format(as.Date(date, format="%Y-%m-%d"), "%Y-%m")) %>%
  filter(date >= date_start & date <= Sys.Date())


hh_site <- hh_site %>%
  filter(!is.na(unit)) %>%
  group_by(site, Month) %>%
  summarise(worker___1 = sum(worker___1),
            worker___2 = sum(worker___2),
            worker___3 = sum(worker___3),
            provider_hands_bef = sum(provider_hands_bef),
            provider_hands_aft = sum(provider_hands_aft),
            nurse_hands_bef = sum(nurse_hands_bef),
            nurse_hands_aft = sum(nurse_hands_aft),
            mt_hands_bef = sum(mt_hands_bef),
            mt_hands_aft = sum(mt_hands_aft))

hh_site <- hh_site %>%
  group_by(site, Month) %>%
  mutate(total_obs = sum(worker___1,worker___2,worker___3),
         total_comp = round((sum(max(provider_hands_bef,provider_hands_aft),
                          max(nurse_hands_bef, nurse_hands_aft),
                          max(mt_hands_bef, mt_hands_aft))/total_obs)*100)) %>%
  dplyr::select(site, Month, total_obs, total_comp)

# network <- data.frame(site = "NETWORK",
#                       Month = "2023-04",
#                       total_obs = 0,
#                       total_comp = 0)
# 
# msw <- data.frame(site = "MSW",
#                       Month = "2023-05",
#                       total_obs = 0,
#                       total_comp = 0)

# msdfp <- data.frame(site = "MSDFP",
#                       Month = "2023-04",
#                       total_obs = 0,
#                       total_comp = 0)

# hh_site <- bind_rows(hh_site, network, msw, msdfp)

hh_site <- hh_site %>%
  arrange(site, Month)

map(unique(hh_site$site), function(x){

    highchart() %>%
  hc_yAxis_multiples(
    list(title = list(text = "Total Observations"), lineWidth = 3),
    list(title = list(text = "% Compliance"), labels = list(format = '{value}%'),
         showLastLabel = FALSE, opposite = TRUE)
  ) %>%
  hc_xAxis(title = list(text = ""),
           categories =(hh_site %>% filter(site == x))$Month,
           # type = "datetime",
           # labels = list(format = '{value:%m/%d}')
           dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name = "Total Observations Submitted",
                data = (hh_site %>% filter(site == x))$total_obs,
                type = 'column',
                color='#00aeef',
                dataLabels = list(enabled = TRUE, format='{point.y}')) %>%
  hc_add_series(name = "% Observations Complied",
                data = (hh_site %>% filter(site == x))$total_comp,
                type = "line", yAxis = 1,
                color='#d80b8c',
                lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE, format='{point.y}%')) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = paste0(x, " - Hand Hygiene Compliance %"), align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  # hc_subtitle(text = paste0("Based on visits from ",date_start," to ",date_end),
  #             align = "left", style = list(fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")
}) %>%
  hw_grid(ncol = 2, rowheight = 400) %>% htmltools::browsable()
  
  
invisible(gc())

```


--------------------------------------------------------------------------------
```{r Hand Hygiene Trending Summarized, echo = FALSE, warning = FALSE, message = FALSE}

hh_downtown <- hh_data_merged %>%
  mutate(Month = format(as.Date(date, format="%Y-%m-%d"), "%Y-%m")) %>%
  filter(date >= date_start & date <= Sys.Date())

hh_downtown <- hh_downtown %>%
  filter(unit != "NULL") %>%
  filter(site %in% c("MSUS","MSDMG","MSBI")) %>%
  mutate(site = "MS Downtown") %>%
  group_by(site, Month) %>%
  summarise(worker___1 = sum(worker___1),
            worker___2 = sum(worker___2),
            worker___3 = sum(worker___3),
            provider_hands_bef = sum(provider_hands_bef),
            provider_hands_aft = sum(provider_hands_aft),
            nurse_hands_bef = sum(nurse_hands_bef),
            nurse_hands_aft = sum(nurse_hands_aft),
            mt_hands_bef = sum(mt_hands_bef),
            mt_hands_aft = sum(mt_hands_aft))

hh_downtown <- hh_downtown %>%
  group_by(site, Month) %>%
  mutate(total_obs = sum(worker___1,worker___2,worker___3),
         total_comp = round((sum(min(provider_hands_bef,provider_hands_aft),
                          min(nurse_hands_bef, nurse_hands_aft),
                          min(mt_hands_bef, mt_hands_aft))/total_obs)*100)) %>%
  dplyr::select(site, Month, total_obs, total_comp)

map(unique(hh_downtown$site), function(x){

  highchart() %>%
  hc_yAxis_multiples(
    list(title = list(text = "Total Observations"), lineWidth = 3),
    list(title = list(text = "% Compliance"), labels = list(format = '{value}%'),
         showLastLabel = FALSE, opposite = TRUE)
  ) %>%
  hc_xAxis(title = list(text = ""),
           categories =(hh_downtown %>% filter(site == x))$Month,
           # type = "datetime",
           # labels = list(format = '{value:%m/%d}')
           dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name = "Total Observations Submitted",
                data = (hh_downtown %>% filter(site == x))$total_obs,
                type = 'column',
                color='#00aeef',
                dataLabels = list(enabled = TRUE, format='{point.y}')) %>%
  hc_add_series(name = "% Observations Complied",
                data = (hh_downtown %>% filter(site == x))$total_comp,
                type = "line", yAxis = 1,
                color='#d80b8c',
                lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE, format='{point.y}%')) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = paste0(x, " - Hand Hygiene Compliance %"), align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  # hc_subtitle(text = paste0("Based on visits from ",date_start," to ",date_end),
  #             align = "left", style = list(fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")
}) %>%
  hw_grid(ncol = 2, rowheight = 400) %>% htmltools::browsable()
invisible(gc())
```



